\Title

### 2020-02-21 manuscript/manuscript.tex
Create target grid figure
Add survey figures
Add LaTeX variables file for synthetic model and surveys
Add single file created by the 01-synthetic-surveys.py notebook where
all quantities related to synthetic model and surveys live.
Import them into the manuscript.

@@

The synthetic model is made out of 64 prisms distributed on a region of
\SI{89}{\km}$\times$\SI{88}{\km} between \SI{10}{\km} deep and the zero
height plane.
Density contrast of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of 56$\times$57 points with a spacing
of \SI{2}{\km} located \SI{2000}{\m} above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
        \SI{2000}{\m} above the zero height plane.
    }
    \label{fig:target-grid}
\end{figure}

@@

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SI{111}{\km}$\times$\SI{111}{\km}.
The ground survey is composed by 963 observation points distributed at heights
ranging between \SI{0}{\m} and \SI{2052}{\m}
(Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has 5673 points at heights between \SI{359}{\m} and
\SI{1255}{\m}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

\begin{figure}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Synthetic airborne survey.
        (a)~Location of observation points.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
        Based upon the Great Britain aeromagnetic data, with the permission of
        the British Geological Survey.
    }
    \label{fig:synthetic-airborne-survey}
\end{figure}

>>>>

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}

@@

The synthetic model is made out of \NPrisms prisms distributed on a region of
\ModelEasting$\times$\ModelNorthing between \ModelDepth deep and the zero
height plane.
Density contrast of prisms range from \ModelMinDensity and \ModelMaxDensity.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of
\TargetEastingSize$\times$\TargetNorthingSize points with a spacing of
\TargetSpacing located \TargetHeight above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of \TargetEastingSize$\times$\TargetNorthingSize points with
        a spacing of \TargetSpacing located \TargetHeight above the zero height
        plane.
    }
    \label{fig:target-grid}
\end{figure}

@@

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SurveyEasting$\times$\SurveyNorthing.
The ground survey is composed by \GroundSurveyPoints observation points distributed at heights
ranging between \GroundSurveyMinHeight and \GroundSurveyMaxHeight
(Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has \AirborneSurveyPoints points at heights between
\AirborneSurveyMinHeight and \AirborneSurveyMaxHeight.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SurveyNoise) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
    \caption{
        Synthetic airborne survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
        Based upon the Great Britain aeromagnetic data, with the permission of
        the British Geological Survey.
    }
    \label{fig:synthetic-airborne-survey}
\end{figure}
